Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2020-08-18 analysis/paper/paper.Rmd
I tried to change the timerange for SPD

spd_test <- modelTest(spd_dates,errors=dates_clean$error,timeRange=c(45000,1000),model='exponential',nsim=200,ncores=3)

summary(spd_test)
plot(spd_test)
```

>>>>

### this code takes long time
spd_test <- modelTest(spd_dates,errors=dates_clean$error,timeRange=c(45000,1000),model='exponential',nsim=200,ncores=3)

summary(spd_test)
plot(spd_test)

# zoom in in on the 40-33ka period GP is trying
spd_test_zoom <- modelTest(spd_dates,errors=dates_clean$error,timeRange=c(40000,33000),model='exponential',nsim=200,ncores=3)
summary(spd_test_zoom)
plot(spd_test_zoom)
```
